Fastest Paths Between Points in $\R^2$ for a Particle Moving with Constant Speed and Bounded Centripetal Acceleration

### 2013-10-10 particle_definitions.tex
Add back figure pdfs.

\begin{definition}
  A particle's speed is $v(t)$, and its direction of motion is $\bhat{v}$.

  A particle with constant speed, is a particle with zero tangential acceleration, $a_t(t) = 0$, and $v(t) = \bar{v}$.
\end{definition}

@@

Before we introduce the equations governing a particle's motion in $\R^2$, we must first define a coordinate system to describe its motion. Unless otherwise specified, the motion of particles in this paper will be described in polar coordinates that contain an extra parameter $\theta$, that is shown in Figure \ref{fig:polar-param}.

\includefig{polar_param.eps}{A particle moving in 2-dimensional polar coordinate system centered at B}{polar-param}

>>>>

\begin{definition}
  A particle's speed is $v(t)$, and its direction of motion is $\bhat{v}$.
\end{definition}

@@

Before we introduce the equations governing a particle's motion in $\R^2$, we must first define a coordinate system to describe its motion. Unless otherwise specified, the motion of particles in this paper will be described in a modified polar coordinate system that contain an extra parameter $\theta$, that is shown in Figure \ref{fig:polar-param}. We will refer to this system as the B centered particle coordinate system.

\includefig{polar_param.eps}{A particle moving in a B centered particle coordinate system}{polar-param}

### 2013-10-10 path_theorems.tex
Add back figure pdfs.

To begin proving things about the fastest path, we first formalize the conditions we will be using:

\begin{definition}
  A fixed speed particle is a particle such that: $\bvec{X} \in \R^2$, $a_t = 0$, $v(t) = \bar{v}$.
\end{definition}

\begin{definition}
  A particle with bounded centripetal acceleration is a particle with the following condition: $\norm{a_c} \le \bar{a_c}$, for some $\bar{a_c} \ge 0$.
\end{definition}

Now we shall use the following shorthand throughout this section to talk about the conditions on a particle:

\begin{definition}
  A particle with constant speed conditions is a fixed speed particle with bounded centripetal acceleration.
\end{definition}

@@

\begin{conjecture}
  \label{conjecture:fastest-paths}
  Let particles $p_1, p_2$ have initial velocities $\bvec{v}_1, \bvec{v}_2$ and starting positions $\bvec{X}_1, \bvec{X}_2$ respectively. Additionally, let $p_1, p_2$ have constant speed conditions and let the end position be $\bvec{X}_f$ such that $d(\bvec{X}_f, \bvec{X}_1) = d(\bvec{X}_f, \bvec{X}_2) > R_{min}$. If $d(\bvec{X}_1, \bvec{X}_f) \leq d(\bvec{X}_2, \bvec{X}_f)$ and $\theta_{p_1}(T_0) < \theta_{p_2}(T_0)$, then $T_f(\bhat{\gamma_1}) < T_f(\bhat{\gamma_2})$.
\end{conjecture}

This conjecture comes from physical intuition. If two particles $p_1$ and $p_2$ are attempting to arrive at a particular ending point $\bvec{X}_f$, and $p_2$ is farther away than $p_1$ and also has an initial angle $\theta$ to $\bvec{X}_f$ that is larger than $p_1$'s initial angle, then $p_2$ must take a longer time to turn towards $\bvec{X}_f$ and must travel a longer distance than $p_1$. Because of this, it seems to be the case that $p_1$'s fastest path is faster than $p_2$'s fastest path.

>>>>

\begin{definition}
  A particle with constant speed, is a particle with zero tangential acceleration, $a_t(t) = 0$, and $v(t) = \bar{v}$.
\end{definition}

\begin{definition}
  A particle with bounded centripetal acceleration is a particle with $\norm{a_c(t)} \le \bar{a_c}$, for some $\bar{a_c} \ge 0$.
\end{definition}

Throughout the rest of this paper, all the particles we will deal with will have constant speed and bounded centripetal acceleration.

@@

\begin{conjecture}
  \label{conjecture:fastest-paths}
  Let particles $p_1, p_2$ have centripetal acceleration bounded by $\bar{a_c}$, constant speed $\bar{v}$, starting positions $\bvec{X}_1, \bvec{X}_2$ respectively, and final position $\bvec{X}_f$. Both particles move in a $X_f$ centered particle coordinate system. If $r_1(T_0) \leq r_2(T_0)$ and $\theta_1(T_0) < \theta_1(T_0)$, then $T_f(\hat{\gamma_1}) < T_f(\hat{\gamma_2})$.
\end{conjecture}

In words, this conjecture states that if a particle, $p_1$, is closer to the final position than another, $p_2$, and has a smaller $\theta(t)$, then its optimal path to the final position is shorter. The intuition behind this is that $p_2$ must travel a longer distance than $p_1$ to reach the final position, because it is further away. Furthermore, one could also imagine, that
